FM project

### 2023-05-07 draft1.Rmd

oecd_crude_oil_agg %>% features(`Amount of Crude Oil (Thousand Barrels)`, features = guerrero)
oecd_crude_oil_agg <- box_cox(oecd_crude_oil_agg$`Amount of Crude Oil (Thousand Barrels)`, 0.28)

oecd_oil_prod_agg %>% features(`Amount of total Petroleum Porducts (Thousand Barrels)`, features = guerrero)
oecd_oil_prod_agg  <- box_cox(oecd_oil_prod_agg$`Amount of total Petroleum Porducts (Thousand Barrels)`, 0.907)

oecd_nat_gas_agg %>% features(oecd_nat_gas_agg$`Amount of Natural gas (BOE)`, features = guerrero)
oecd_nat_gas_agg <- box_cox(oecd_nat_gas_agg$`Amount of Natural gas (MMcf)`, 1.13)

>>>>

lambda1 <- oecd_crude_oil_agg %>% 
  features(`Amount of Crude Oil (Thousand Barrels)`, features = guerrero) %>% 
  pull(lambda_guerrero)
crude_oil_agg <- oecd_crude_oil_agg %>% 
  mutate(`Amount of Crude Oil (Thousand Barrels)` = box_cox(`Amount of Crude Oil (Thousand Barrels)`, lambda1))

lambda2 <- oecd_oil_prod_agg %>% 
  features(`Amount of total Petroleum Porducts (Thousand Barrels)`, features = guerrero) %>% 
  pull(lambda_guerrero)
oil_prod_agg <-oecd_oil_prod_agg %>% 
  mutate(`Amount of total Petroleum Porducts (Thousand Barrels)` = box_cox(`Amount of total Petroleum Porducts (Thousand Barrels)`, lambda2))

lambda3 <- oecd_nat_gas_agg %>% 
  features(`Amount of Natural gas (BOE)`, features = guerrero) %>% 
  pull(lambda_guerrero)
nat_gas_agg <- oecd_nat_gas_agg %>% 
  mutate(`Amount of Natural gas (BOE)` = box_cox(`Amount of Natural gas (BOE)`, lambda3))
